Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-24 cav2017/cav2017.tex
reviewed 3.3 Stability of closed-loop systems

Asymptotic stability boils down to Lyapunov stability and convergence to an equilibrium point~\cite{Astrom08}.  %\todo{add reference}.  
Lyapunov stability requires that model trajectories remain in a neighbourhood of the equilibrium point. 
In the case of closed-loop LTI models as in \eqref{eq:closedloopss}, 
the equilibrium point is the origin (if the reference is equal to zero), or an offset thereof.  
In this paper, we consider systems with a reference signal equal to zero.

A discrete-time system as \eqref{eq:closedloopss} is asymptotically stable if and only if all the roots 
of the characteristic polynomial ({\it i.e.}, the eigenvalues of the closed-loop matrix $A_d - B_d K$) are inside the unity circle in the complex plane, 
{\it i.e.} iff their absolute values are less than one~\cite{astrom1997computer}. 
In this paper, we express the stability specification $\phi_{stability}$ in terms of a check known as Jury's criterion \cite{fadali}. 
This condition boils down to an easy algebraic formula to select the entries of matrix $K$, 
so that the closed-loop dynamics are shaped as desired. 
A detailed description of this specification can be found in the Appendix~\ref{sec:appendix-stability}.

>>>>

Asymptotic stability boils down to Lyapunov stability 
and convergence to an equilibrium point~\cite{Astrom08}. 
Lyapunov stability requires that model trajectories remain i
n a neighborhood of the equilibrium point. 
In the case of closed-loop LTI models as in \eqref{eq:closedloopss}, 
the equilibrium point is the origin (if the reference is equal to zero), 
or an offset thereof. Here, we consider systems with a zero reference signal.

A discrete-time system as \eqref{eq:closedloopss} is asymptotically stable 
\textit{iff} all the roots of the characteristic polynomial 
(i.e., the eigenvalues of the closed-loop matrix $A_d - B_d K$) 
are inside the unity circle in the complex plane, i.e., \textit{iff} their absolute 
values are less than one~\cite{astrom1997computer}. 
In this paper, we express the stability specification $\phi_{stability}$ 
in terms of a check known as Jury's criterion~\cite{fadali}. 
This condition boils down to an easy algebraic formula to select the entries 
of matrix $K$, so that the closed-loop dynamics are shaped as desired. 
A detailed description of this specification can be found in the 
Appendix~\ref{sec:appendix-stability}.
